### 2015-07-31 Docs/getting_started/getting_started.tex
more on mini plotfiles

Some of the test problems available are:
\begin{itemize}
\item {\tt incomp\_shear\_jet} \\[-3mm]

@@

@@

@@

>>>>

Some of the test problems available are:
\begin{itemize}
\item {\tt double\_bubble} \\[-3mm]

A rising bubble problem where the bubble(s) can have a different gamma
than the surrounding atmosphere.  This uses the {\tt multigamma} EOS.

\item {\tt incomp\_shear\_jet} \\[-3mm]

@@

\item {\tt flame\_1d} \\[-3mm]

   A 1-d version of the {\tt flame} problem above.  This uses a special
   elliptic solver in \boxlib\ that only works for a single grid, so
   no parallel runs are allowed for this problem.

@@

\item \runparam{plot\_base\_name} is the basename to use for the
  plotfile filename.  The step number will be appended to
  this name.

@@

Note that in addition to the normal plotfiles, there are {\em mini} plotfiles
that store a small subset of the fields, intended to be output more frequently.
These are described in \S~\ref{vis:sec:miniplotfile}.

### 2015-07-31 Docs/visualization/visualization.tex
more on mini plotfiles

\subsection{Mini vs.\ regular plotfiles}

@@

\begin{itemize}
\item {\tt mini\_plot\_int} is the interval in steps between successive plotfiles
\item {\tt mini\_plot\_deltat} is the interval in time between successive plotfiles
\item {\tt mini\_plot\_base\_name} is the base name that prefixes the plotfiles.  The
  default is {\tt miniplt}
\end{itemize}

To set the fields that are stored in the mini plotfile, a second set
of runtime parameters is used: {\tt mini\_plot\_var1}, {\tt
  mini\_plot\_var2}, $\ldots$, {\tt mini\_plot\_var9}.  These can be set to
any of the following:
\begin{itemize}
  \item {\tt "density"}
  \item {\tt "species"}: this gets all of the mass fractions
  \item the name of an individual species in the network (like {\tt "helium-4"})
  \item {\tt "radvel"}: this gets both the radial and circumferential velocity
  \item {\tt "velocity"}: all three componets
  \item {\tt "temperature"}: this is either $T(\rho,p_0)$ or $T(\rho,h)$, depending
    on the value of {\tt use\_tfromp}
  \item {\tt "enuc"}: the nuclear energy generation rate
  \item {\tt "mach"}: the Mach number
\end{itemize}

>>>>

\subsection{Mini vs.\ regular plotfiles}
\label{vis:sec:miniplotfile}

@@

\begin{itemize}
\item \runparam{mini\_plot\_int} is the interval in steps between successive plotfiles
\item \runparam{mini\_plot\_deltat} is the interval in time between successive plotfiles
\item \runparam{mini\_plot\_base\_name} is the base name that prefixes the plotfiles.  The
  default is {\tt miniplt}
\end{itemize}

To set the fields that are stored in the mini plotfile, a second set
of runtime parameters is used: \runparam{mini\_plot\_var1}, {\tt
  mini\_plot\_var2}, $\ldots$, {\tt mini\_plot\_var9}.  These can be set to
any of the following:
\begin{itemize}
  \item {\tt "density"}
  \item {\tt "species"}: this gets all of the mass fractions
  \item the name of an individual species in the network (like {\tt "helium-4"})
  \item {\tt "radvel"}: this gets both the radial and circumferential velocity
  \item {\tt "velocity"}: all three componets
  \item {\tt "temperature"}: this is either $T(\rho,p_0)$ or $T(\rho,h)$, depending
    on the value of {\tt use\_tfromp}
  \item {\tt "enuc"}: the nuclear energy generation rate
  \item {\tt "mach"}: the Mach number
\end{itemize}
